### 2025-12-10 submissions/03-jpam-RR/manuscript_online_appendix.tex
submit R&R!

@@

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004--2021 Current Population Survey.}}
    \end{figure}

\subsection*{Using \textcite{lubotskyInterpretationRegressionsMultiple2006} to Construct Bias Index} % (fold)
\label{sub:lw-bias}
In \textcite{lubotskyInterpretationRegressionsMultiple2006}, the authors propose a method to reduce measurement error in proxies by constructing a composite index. The Lubotsky-Wittenberg (henceforth LW) consider a model where a covariate is unobserved. Therefore, they use two proxies in its place, which will have measurement error. Thus, the LW method allows researchers to use two proxies that are error-ridden.

>>>>

% =========================
% Implicit association test examples
% =========================

@@

% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (All Generations)}
% \label{fig:pp-all-gen}

% \begin{subfigure}{.48\textwidth}
% \caption{Anti-Asian Bias}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_all_generations_value.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{Female}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_all_generations_Female.png}
% \end{subfigure}

% \vspace{0.5cm}

% \begin{subfigure}{.48\textwidth}
% \caption{College Graduate: Mother}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_all_generations_MomGradCollege.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{College Graduate: Father}
% \centering
% \includegraphics[width=1\linewidth]{boot_pp_all_generations_DadGradCollege.png}
% \end{subfigure}

% \caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. The analysis includes first-, second-, and third-generation Asian Americans. First-generation Asian Americans are foreign-born individuals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent. Third-generation Asian Americans are native-born individuals with native-born parents and at least one Asian-born grandparent. Each curve reports the median predicted probability across 1{,}000 bootstrap resamples, and 95\% confidence intervals use the percentile method from the same draws.}}
% \end{figure}
% \end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second-Generation Asian Americans with Asian Fathers and White Mothers)}
\label{fig:pp-second-aw}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_Female.png}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_AW_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, and 95\% confidence intervals follow the corresponding bootstrap percentile limits.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second-Generation Asian Americans with White Fathers and Asian Mothers)}
\label{fig:pp-second-wa}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_Female.png}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_second_WA_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of second-generation Asian Americans with White fathers and Asian mothers. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, and 95\% confidence intervals follow the corresponding bootstrap percentile limits.}}
\end{figure}
\end{center}

% =========================
% 41: Multinomial Model - Predicted Probabilities (Adults, AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Anti-Asian Bias and Gender (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa}

% Top row: Anti-Asian Bias and Female
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_value.png}\label{subfig:pp-secgen-aw-bias}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_value.png}\label{subfig:pp-secgen-wa-bias}
\end{subfigure}

% Second row: Female
\begin{subfigure}{.48\textwidth}
\caption{Female (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_Female.png}\label{subfig:pp-secgen-aw-female}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_Female.png}\label{subfig:pp-secgen-wa-female}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of anti-Asian bias or gender, holding other covariates at their means. Curves plot the median predicted probability across 1{,}000 bootstrap resamples, with 95\% confidence intervals given by the bootstrap percentile bounds.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Years of Education and Income (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa-2}

% Top row: EducYears
\begin{subfigure}{.48\textwidth}
\caption{Years of Education (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_EducYears.png}\label{subfig:pp-secgen-aw-EducYears}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Years of Education (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_EducYears.png}\label{subfig:pp-secgen-wa-EducYears}
\end{subfigure}

% Second row: lnftotval
\begin{subfigure}{.48\textwidth}
\caption{Log Family Income (AW)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_AW_adults_multinom_lnftotval.png}\label{subfig:pp-secgen-aw-lnftotval}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Log Family Income (WA)}
\centering
\includegraphics[width=1\linewidth]{logit_boot_pp_second_WA_adults_multinom_lnftotval.png}\label{subfig:pp-secgen-wa-lnftotval}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of total years of education or log family income, holding other covariates at their means. Curves plot the median predicted probability across 1{,}000 bootstrap resamples, with 95\% confidence intervals given by the bootstrap percentile bounds.}}
\end{figure}
\end{center}

% =========================
% Multinomial Model - Predicted Probabilities Third Gens
% =========================

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with One Asian Grandparent)}
\label{fig:pp-third-one}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_Female.png}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_oneAsian_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with one Asian grandparent. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Third-Generation Asian Americans with Two Asian Grandparents)}\label{fig:pp-third-two}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_value.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_Female.png}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_MomGradCollege.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{boot_pp_third_twoAsian_DadGradCollege.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from estimating equation (\ref{eq:multinomial_logit}) using a multinomial logit model for the subsample of third-generation Asian Americans with two Asian grandparents. The model estimates the probability of choosing ``Asian only'', ``White only'', or ``Asian and White'' racial identification as a function of anti-Asian bias, gender, and parental education. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. All other variables are held at their sample means. Reported curves depict the median predicted probability across 1{,}000 bootstrap resamples, with 95\% percentile confidence intervals from the same draws.}}
\end{figure}
\end{center}

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004--2021 Current Population Survey.}}
    \end{figure}    
\subsection*{Using \textcite{lubotskyInterpretationRegressionsMultiple2006} to Construct Bias Index} % (fold)
\label{sub:lw-bias}
In \textcite{lubotskyInterpretationRegressionsMultiple2006}, the authors propose a method to reduce measurement error in proxies by constructing a composite index. The Lubotsky-Wittenberg (henceforth LW) consider a model where a covariate is unobserved. Therefore, they use two proxies in its place, which will have measurement error. Thus, the LW method allows researchers to use two proxies that are error-ridden.
